---
title: "CodeBook"
author: "Brett Taylor"
date: "February 13, 2015"
output:
  word_document:
    fig_caption: yes
    highlight: tango
  md_document:
    variant: markdown_github
  pdf_document: default
  html_document:
    number_sections: yes
---
##Study Design 
### The steps to producing the data set. 
 variables, the data, and any transformations or work that you performed to clean up the data 
Transformations
Variables

###Reference:
[1] Davide Anguita, Alessandro Ghio, Luca Oneto, Xavier Parra and Jorge L. Reyes-Ortiz. Human Activity Recognition on Smartphones using a Multiclass Hardware-Friendly Support Vector Machine. International Workshop of Ambient Assisted Living (IWAAL 2012). Vitoria-Gasteiz, Spain. Dec 2012

##Code Book
###Includes a list of the variables 



##Functions

```{r, echo=FALSE,comment=NA}
functions<-read.csv("functions.csv")
 print(functions,row.names=FALSE)

```
******
##Variables
The variables included in this data set follow a naming pattern that can help you understand its nature.  

Column       |  Description
------------- | -------------------
variable_name | This the name of the column displayed in the summary data set.
feature_id    | This is the identifier associated with the feature
domain:       | na 
measure       | na 
Function      | na
dimension     | na

```{r, echo=FALSE,out.width=300,comment=NA}
td<-read.table("activity-measurement-by-subject.txt",header = TRUE)
variables<-names(td)
feature_index<-regexpr("([0-9][0-9][0-9])",variables)
features <- rep(NA,length(feature_index))       
features[feature_index!=-1]<-regmatches(variables,feature_index)

domain_index<-regexpr("(time|frequency)",variables)
domains <- rep(NA,length(domain_index))
domains[domain_index!=-1] <- regmatches(variables, domain_index)

#domains<-gsub("fid[0-9][0-9][0-9]_(time|frequency|angle_)","",variables)
measure_index<-regexpr("(BodyAcc|GravityAcc|BodyAccJerk|BodyGyro|BodyGyroJerk|BodyAccMag|GravityAccMag|BodyAccJerkMag|BodyGyroMag|BodyGyroJerkMag)",variables)
measures <- rep(NA,length(measure_index))       
measures[measure_index!=-1]<-regmatches(variables,measure_index)

calc_index<-regexpr("(mean|std|meanFreq)",variables)
calculations <- rep(NA,length(calc_index))       
calculations[calc_index!=-1]<-regmatches(variables,calc_index)

dim_index<-regexpr("[XYZ]|angle",variables)
dims <- rep(NA,length(dim_index))       
dims[dim_index!=-1]<-regmatches(variables,dim_index)

variable.definitions<-as.data.frame(cbind(Variable.Name=variables,Feature.Id=features,Domain=domains,Measure=measures,Function=calculations,Dimension=dims))
print(variable.definitions,row.names = FALSE)


```


### License:

Use of this dataset in publications must be acknowledged by referencing the following publication [1] 

[1] Davide Anguita, Alessandro Ghio, Luca Oneto, Xavier Parra and Jorge L. Reyes-Ortiz. Human Activity Recognition on Smartphones using a Multiclass Hardware-Friendly Support Vector Machine. International Workshop of Ambient Assisted Living (IWAAL 2012). Vitoria-Gasteiz, Spain. Dec 2012

This dataset is distributed AS-IS and no responsibility implied or explicit can be addressed to the authors or their institutions for its use or misuse. Any commercial use is prohibited.

Jorge L. Reyes-Ortiz, Alessandro Ghio, Luca Oneto, Davide Anguita. November 2012.


