---
title: "CodeBook"
author: "Brett Taylor"
date: "February 22, 2015"
output:
  
  md_document:
    variant: markdown_github
  pdf_document: default
  html_document: default
  word_document:
    fig_caption: yes
    highlight: tango
  
---
##Study Design 
### The steps to producing the data set. 
_Processing Overview_
The script was developed to properly load the data, and process it in a simplified method.  The following are the steps taken to retrieve, and clean the data.  The script that performed this process is found in the file "run_analysis.txt" 

__1  Clean Feature names__     

The process includes first, reading in the feature\_names, and cleaning them up.  The feature names that were included in the data from the file features.txt had several issues, including duplicate names, embedding of characters that would not work well as column names,  and abbreviations that are difficult to understand.  A function, normalize.features() is created that replaces these issues with more detail.  I also created a prefix _fid[0-9,0-9,0-9]_  that includes the feature identifier from the source features.txt file.  This allows for simplified tracing of the data back to the source.

__2  Read Source Data__   
The next step is to read in all of the source data files.  The files that were required include the following:

File                 |Obs # |  Description
---------------------|------|-------------
subject_train.txt    |7352  | This associates the subject identifier with the x and y training observations.
subject_test.txt     |2947  | This associates the subject identifier with the x and y testing observations.
X_train.txt          |7352  | 561 feature measurement columns for each observation. This is the data was sampled for ML training.  
X_test.txt           |2947  | 561 feature measurement columns for each observation. This is the data was sampled for testing the outcome of the ML training.
y_train.txt          |7352  | This includes a single attribute that represents the activity code. This is the data was sampled for ML training.  
y_test.txt           |2947  | This includes a single attribute that represents the activity code. This is the data was sampled for testing the outcome of the ML training.
features.txt         | 561  | This includes columns for feature identifier, and the feature description.    
activity.txt         | 6    | Columns include activity id, and activity description.  
__activity_summary.txt__|180   | The final summarized output file that includes the average of the mean, and standard deviation features aggregated by Activity and Subject.

__3  Combine & Merge data frames__  

  First combine the columns together from each of the data sets.  This creats a test and training data set.
  Next combine the the test and training data set.  
  
  Output: data.frame all.data
  
__4  Label all.data__     

  Add the activity labels to the all.data dataframe.  

Output: data.frame all.data.labeled
  
_5_ __Select the correct variables for all.data.labeled__
   Only keep the columns that are the subject, activity, and those that include the mean or standard deviation.  The decision was made to not include angle measurements because they are synthesis of other vectors that happen to have the term mean in their name.  Use regular expressions to eliminate the other columns.    

Output: data.frame all.data.labeled    
__6  __Summarize all.data.labeled__   

  Create a summary of the aggregates grouped by Activity and Subject.  Apply to function mean() to all of the numeric measurement columns. 
  Sort the data by Activity, and Subject
  
  Output: data.frame tidy.data   
  
__7  Write tidy.data to file__   
  This file is the final output that contains the summary data from the tidy.data dataframe.  The activity_summary file meets the requirements of the Course project 5 step (see above).
  
  Output: file "activity_summary.txt"   

###Reference:
[1] Davide Anguita, Alessandro Ghio, Luca Oneto, Xavier Parra and Jorge L. Reyes-Ortiz. Human Activity Recognition on Smartphones using a Multiclass Hardware-Friendly Support Vector Machine. International Workshop of Ambient Assisted Living (IWAAL 2012). Vitoria-Gasteiz, Spain. Dec 2012

##Code Book
###Includes a list of the variables 



##Functions

```{r, echo=FALSE,comment=NA}
functions<-read.csv("functions.csv")
 print(functions,row.names=FALSE)

```
******
##Variables
The variables included in this data set follow a naming pattern that can help you understand its nature.  

Column       |  Description
------------- | -------------------
variable_name | This the name of the column label displayed in the activity_summary.txt data set.
feature_id    | This is the identifier associated with the feature.txt file.  It will allow you to trace back to the source column in the X_(train|test).txt file.
domain:       | the measures were are either in the time or frequency domain. This was translated from -f for frequency, or a -t time.  The frequency domain was converted from the signal data by fourier transform in the initial data sets.
signal       | The measure is based on the following values {BodyAcc,BodyAccJerk, BodyGyro,BodyGyroJerk,BodyAccMag,BodyAccJerk,BodyGyroMag,BodyGyroJerkMag,GravityAcc,GravityAccMag}.  Acc==Acceleration, Gyro=Gyration
Function      | The functions applied to the signals.  The list that were selected are mean(),std(),meanFreq().
dimension     | This indicates the direction of the vector.  values are {X,Y,Z}

*****

```{r, echo=FALSE,out.width=300,comment=NA}
library(dplyr,quietly = TRUE,warn.conflicts = FALSE)
td<-read.table("activity-summary.txt",header = TRUE)
variables<-names(td)
feature_index<-regexpr("([0-9][0-9][0-9])",variables)
features <- rep(NA,length(feature_index))       
features[feature_index!=-1]<-regmatches(variables,feature_index)

domain_index<-regexpr("(time|frequency)",variables)
domains <- rep(NA,length(domain_index))
domains[domain_index!=-1] <- regmatches(variables, domain_index)

measure_index<-regexpr("(BodyAcc|GravityAcc|BodyAccJerk|BodyGyro|BodyGyroJerk|BodyAccMag|GravityAccMag|BodyAccJerkMag|BodyGyroMag|BodyGyroJerkMag)",variables)
measures <- rep(NA,length(measure_index))       
measures[measure_index!=-1]<-regmatches(variables,measure_index)

calc_index<-regexpr("(mean|std|meanFreq)",variables)
calculations <- rep(NA,length(calc_index))       
calculations[calc_index!=-1]<-regmatches(variables,calc_index)

dim_index<-regexpr("[XYZ]|angle",variables)
dims <- rep(NA,length(dim_index))       
dims[dim_index!=-1]<-regmatches(variables,dim_index)
variable.definitions<-as.data.frame(cbind(Variable.Name=variables,Feature.Id=features,Domain=domains,Signal=measures,Function=calculations,Dimension=dims))
first<-select(variable.definitions,matches("Variable.Name|Feature.Id|Dimension")) 
second<-select(variable.definitions,one_of("Variable.Name","Domain","Signal")) 
#print(second,row.names=FALSE)

#print(variable.definitions,row.names = FALSE)
#print.variable.data<-function(row)
#        {(paste("Variable: ",row[1],sep=": "))}
#results<-as.vector(apply(variable.definitions,1,print.variable.data))


```


This activity_summary.txt file has a total of `r nrow(td)` observations, and `r length(names(td))` columns.

### Primary Variables

* __Subject__

        This is an integer in the range 1:30 of the subjects that were engaged in the experiment.
* __Activity__
        This is the type of action the subject was performing during the measurement.   Values range from
{Laying,Sitting,Standing, Walking,Walking_Downstairs,Walking_Upstairs}

###Signal Variable Descriptions - Variable, Feature.Id and Dimension

The following is a description of the fields:  
```{r,echo=FALSE}
print(first,row.names=FALSE)
```
###Signal Variable Descriptions (cont.) - Variable, Domain and Signal
```{r,echo=FALSE}
print(second,row.names=FALSE)
```

## Note
It was attended that the variable descriptions would be in a single table.  This had to be modified due to issues with the ability to fit the six columns in a single table.  This will be researched in the future.

# License

Use of this dataset in publications must be acknowledged by referencing the following publication [1] 

[1] Davide Anguita, Alessandro Ghio, Luca Oneto, Xavier Parra and Jorge L. Reyes-Ortiz. Human Activity Recognition on Smartphones using a Multiclass Hardware-Friendly Support Vector Machine. International Workshop of Ambient Assisted Living (IWAAL 2012). Vitoria-Gasteiz, Spain. Dec 2012

This dataset is distributed AS-IS and no responsibility implied or explicit can be addressed to the authors or their institutions for its use or misuse. Any commercial use is prohibited.

Jorge L. Reyes-Ortiz, Alessandro Ghio, Luca Oneto, Davide Anguita. November 2012.


