---
title: "Read.Me"
author: "Brett Taylor"
date: "February 22, 2015"
output: 
md_document:
        variant: markdown_github
---


link here [A Public Domain Dataset for Human Activity Recognition Using Smartphones][doc1]




```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

==================================================================
Human Activity Recognition Using Smartphones Dataset
Version 1.0
==================================================================
Jorge L. Reyes-Ortiz, Davide Anguita, Alessandro Ghio, Luca Oneto.
Smartlab - Non Linear Complex Systems Laboratory
DITEN - Universit? degli Studi di Genova.
Via Opera Pia 11A, I-16145, Genoa, Italy.
activityrecognition@smartlab.ws
www.smartlab.ws
==================================================================

[doc1]: https://www.elen.ucl.ac.be/Proceedings/esann/esannpdf/es2013-84.pdf "A Public Domain Dataset for Human Activity Recognition Using Smartphones"
